Estimating duration in the presence of misclassification

### 2024-03-12 cis-imperfect-testing.tex
fix mistake in text

Next, I considered the consequence of $\psens$ being misspecified, using the vague prior; the better performing prior in the correctly specified case.
If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates.
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is overestimated.
This effect dominates over the opposing bias of overestimating the number of missed episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    True survival time shown in black.
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence, (B) is correctly specified but (A) and (C) have misspecified $\psens$.
  }
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}

>>>>

Next, I considered the consequence of $\psens$ being misspecified, using the model combination prior; the better performing prior in the correctly specified case.
If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates.
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is overestimated.
This effect dominates over the opposing bias of overestimating the number of missed episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    True survival time shown in black.
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence, (B) is correctly specified but (A) and (C) have misspecified $\psens$.
  }
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}
